Abstract Data Type Inference

### 2015-03-22 histories.tex
Small typo fix.
More examples + citation to interval orders.

  \item $<$ is a partial \emph{happens-before} order on $O$,

@@

  We draw histories by writing one operation per line, starting with its
  operation identifier and match target, followed by its method label,
  possibly a read-only marker, and its happens-before interval. For instance,
  in the history
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)    #
\end{verbatim}
  Operation~$1$ is a write operation which matches itself, and precedes a
  read-only read operation which also targets Operation~$1$. Note that we
  only label method argument and return values for illustrative purposes only;
  histories do not keep them. In the following history, Operations~$1$ and~$2$
  execute concurrently
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)  #
    [3:X] read => b (RO)    #
    [4:_] read*     (RO)      #
\end{verbatim}
  Operation~$3$ is unmatched, and Operation~$4$ is pending.

@@

  TODO MATCHING SCHEME EXAMPLE

@@

\end{itemize}
We denote the set $\set{H(e,M,R) : e \in E}$ of histories of an execution set
$E$ by $H(E,M,R)$.

@@

  The histories of the Executions of Example~\ref{ex:executions} are
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)      #
\end{verbatim}
  in which all three operations are sequential,
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)        #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the first two operations overlap, and
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the last two operations overlap.
  TODO SAY SOMETHING INTERESTING IN THIS EXAMPLE
\end{example}

@@

In Section~\ref{sec:nature} we demonstrate faithful matching schemes for the
executions of naturally-occurring ADTs, and in Section~\ref{sec:matching} we
demonstrate how to infer faithful matching schemes. Otherwise, for the
remainder of this work, we assume each set of executions comes equipped with a
faithful matching scheme $\tup{M,R}$, and abbreviate $H(E,M,R)$ by $H(E)$.

>>>>

  \item $<$ is a \emph{happens-before} interval order\footnote{An interval
  order~\cite{books/Fishburn85} is a partial order whose elements can be mapped
  to integral intervals preserving the order relation, or equivalently, a
  partial order for which $w < x$ and $y < z$ implies $w < z$ or $y < x$.} on
  $O$,

@@

\begin{example}
  \label{ex:histories}

  We draw histories by writing one operation per line, starting with its
  operation identifier and match target, followed by its method label,
  possibly a read-only marker, and its happens-before interval. For instance,
  in the history
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)    #
\end{verbatim}
  Operation~$1$ is a write operation which matches itself, and precedes a
  read-only read operation which also targets Operation~$1$. Note that we
  label method argument and return values for illustrative purposes only;
  histories do not keep them. In the following history, Operations~$1$ and~$2$
  execute concurrently
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)  #
    [3:X] read => b (RO)    #
    [4:_] read*     (RO)      #
\end{verbatim}
  Operation~$3$ is unmatched, indicated by the {\tt X}, and Operation~$4$ is
  pending, indicated by the {\tt *} on its label.

@@

\begin{example}
  \label{ex:matching}

  Consider the following matching scheme for the read and write operations of
  a single-value register object:
  \begin{itemize}

    \item write$(v)$ operations match themselves, and

    \item read $\Rightarrow v$ operations are read-only, and match themselves
    when they return $v = \mathord\perp$, or a write$(v)$ operation, if one
    exists, and otherwise have no match,

  \end{itemize}
  which is well defined when each value $v \in \mathbb{V}$ appears as the
  argument of at most one write operation in any execution. This matching
  scheme corresponds to the matching functions in the histories of
  Example~\ref{ex:histories}.

@@

\end{itemize}
We denote the set $\set{H(e,M,R) : e \in E}$ of histories of an execution set
$E$ by $H(E,M,R)$. When the matching scheme $\tup{M,E}$ is clear from the
context, we abbreviate $H(e,M,R)$ and $H(E,M,R)$ by $H(e)$ and $H(E)$.

@@

  The histories of the executions of Example~\ref{ex:executions} according to
  the matching scheme of Example~\ref{ex:matching} are $H(e_1)$:
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)      #
\end{verbatim}
  in which all three operations are sequential, $H(e_2)$:
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)        #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the first two operations overlap, and $H(e_3)$:
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the last two operations overlap.

@@

In Section~\ref{sec:nature} we demonstrate faithful matching schemes for the
executions of naturally-occurring ADTs, and in Section~\ref{sec:matching} we
demonstrate how to infer faithful matching schemes. Otherwise, for the
remainder of this work, we assume each set of executions comes equipped with a
faithful matching scheme $\tup{M,R}$.
